Quality measure notes

### 2021-07-14 StateOfPractice/Ao-Report/12Background.tex
ao report - update ch 2

This chapter introduces several different categories of software, based on which we designed the processes to select the software domain and software candidates in Chapter \ref{ch_methods}. It also covers the software quality definitions used in the grading template in Appendix \ref{ap_grading_template} and an overview of the Analytic Hierarchy Process (AHP), a tool we used to compare and grade software products.

\section{Software Categories}
We usually target specific software categories to narrow down the scopes when selecting software domains and software packages. In this section, we discuss three common software categories that are mentioned in Section \ref{sec_software_selection}, and also SC software. Section \ref{sec_domain_selection} and Section \ref{sec_software_selection} present more details about why we prefer some of these categories.

@@

The definitions of software qualities are from Smith et al. \cite{SmithEtAl2020}. The order of the qualities follows the grading template in Appendix \ref{ap_grading_template}.

>>>>

When designing a method for evaluating the state of the practice of domain-specific software, we included a step to select domain and software. Knowledge of different software categories is essential for the selections. To compare and grade the software qualities with the grading template in Appendix \ref{ap_grading_template}, we need the definitions of qualities and the Analytic Hierarchy Process (AHP).

\section{Software Categories}
We usually target specific software categories to narrow down the scopes when selecting software domains and software packages. In this section, we discuss three common software categories and also SC software.

@@

Our grading template in Appendix \ref{ap_grading_template} contain nine software qualities. This section lists the definitions of them, which are from Smith et al. \cite{SmithEtAl2020}. The order of the qualities follows the grading template.
